Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-08 manuscript.Rmd
fewer metrics

```{r metrics, warning=FALSE, fig.cap="Metrics", fig.align="center", fig.width=5, fig.height=8, cache=TRUE, cache.extra=tools::md5sum("data/group_split_metrics.csv")}
metrics <- read_csv("data/group_split_metrics.csv") %>% 
  filter(model %in% c("group", "split")) %>% 
  mutate(Model = factor(model, levels = c("group", "split"), labels = c("Group", "Individual")))

@@

metric_plot <- function(ds, met) {
  ds %>% filter(metric == met) %>% 
    ggplot(aes(x = Model, y = value)) + 
    geom_sina(alpha = .7, fill = "turquoise3", size = 4, maxwidth = .5, shape = 21) +
    stat_summary(fun = "mean", mapping = aes(x = Model, y = value), shape = "-", fill = "black", size = 4) + 
    ylim(0, 1) + ylab(met) + xlab("") + 
    theme(plot.title.position = "plot",
          axis.title.y = element_text(size = 13),
          axis.text.y = element_text(size = 11),
          axis.text.x = element_text(size = 13))
}
metric_labels <- c("Overall Accuracy", "Balanced Accuracy", "F1", "Sensitivity", "Pos Pred Value", "Kappa")
title_labels <- c("A. Overall Accuracy", "B. Balanced Accuracy", "C. F1 Score", "D. Sensitivity", "E. Pos. Pred. Value", "F. Kappa")
metric_plots <- map(metric_labels, ~ metric_plot(metrics_long, .x)) %>% map2(., title_labels, ~.x + ggtitle(.y))
(metric_plots[[1]] + metric_plots[[2]])/(metric_plots[[3]]+metric_plots[[4]])/(metric_plots[[5]] + metric_plots[[6]])

@@

<!-- GET RID OF BALANCED ACCURACY AND F1, MOVE KAPPA UP, THEN DO SENS/PPV -->
Figure \@ref(fig:metrics) and Table \@ref(tab:metrics-table) summarize the performance of group and individual models using standard metrics for classification. Overall accuracy (Figure \@ref(fig:metrics)A) represents the proportion of 4-s windows in the testing set in which the model prediction matched the human annotation of body position. Median overall accuracy was `r metrics_lookup["Overall Accuracy", "median_Group"]` for group models and `r metrics_lookup["Overall Accuracy", "median_Individual"]` for individual models. Although individual model accuracy was greater than group model accuracy, group model accuracy approached the level of agreement found between two human coders (median = .92) indicating that group models could adequately replace human coders. Still, it is notable that the worst-case accuracy from group models (minimum = `r metrics_lookup["Overall Accuracy", "min_Group"]`) was considerably lower than in individual models (minimum = `r metrics_lookup["Overall Accuracy", "min_Individual"]`). Possibly, individual models accounted for idiosyncrasies in behavior or inconsistencies in sensor placement for those sessions that group models could not generalize to.

>>>>

```{r metrics, warning=FALSE, fig.cap="Metrics", fig.align="center", fig.width=5.5, fig.height=5.5, cache=TRUE, cache.extra=tools::md5sum("data/group_split_metrics.csv")}
metrics <- read_csv("data/group_split_metrics.csv") %>% 
  filter(model %in% c("group", "split")) %>% 
  mutate(Model = factor(model, levels = c("group", "split"), labels = c("Group", "Individual")))

@@

metric_plot <- function(ds, met) {
  ds %>% filter(metric == met) %>% 
    ggplot(aes(x = Model, y = value)) + 
    geom_sina(alpha = .7, fill = "turquoise3", size = 4, maxwidth = .5, shape = 21) +
    stat_summary(fun = "mean", mapping = aes(x = Model, y = value), shape = "-", fill = "black", size = 4) + 
    ylim(0, 1) + ylab(met) + xlab("") + 
    theme(plot.title.position = "plot",
          axis.title.y = element_text(size = 13),
          axis.text.y = element_text(size = 11),
          axis.text.x = element_text(size = 13))
}
# metric_labels <- c("Overall Accuracy", "Balanced Accuracy", "F1", "Sensitivity", "Pos Pred Value", "Kappa")
# title_labels <- c("A. Overall Accuracy", "B. Balanced Accuracy", "C. F1 Score", "D. Sensitivity", "E. Pos. Pred. Value", "F. Kappa")
metric_labels <- c("Overall Accuracy", "Kappa", "Sensitivity", "Pos Pred Value")
title_labels <- c("A. Overall Accuracy", "B. Kappa", "C. Sensitivity", "D. Pos. Pred. Value")
metric_plots <- map(metric_labels, ~ metric_plot(metrics_long, .x)) %>% map2(., title_labels, ~.x + ggtitle(.y))
(metric_plots[[1]] + metric_plots[[2]])/(metric_plots[[3]]+metric_plots[[4]])
# (metric_plots[[1]] + metric_plots[[2]])/(metric_plots[[3]]+metric_plots[[4]])/(metric_plots[[5]] + metric_plots[[6]])

@@

Figure \@ref(fig:metrics) and Table \@ref(tab:metrics-table) summarize the performance of group and individual models using standard metrics for classification. Overall accuracy (Figure \@ref(fig:metrics)A) represents the proportion of 4-s windows in the testing set in which the model prediction matched the human annotation of body position. Median overall accuracy was `r metrics_lookup["Overall Accuracy", "median_Group"]` for group models and `r metrics_lookup["Overall Accuracy", "median_Individual"]` for individual models. Although individual model accuracy was greater than group model accuracy, group model accuracy approached the level of agreement found between two human coders (median = .92) indicating that group models could adequately replace human coders. Still, it is notable that the worst-case accuracy from group models (minimum = `r metrics_lookup["Overall Accuracy", "min_Group"]`) was considerably lower than in individual models (minimum = `r metrics_lookup["Overall Accuracy", "min_Individual"]`). Possibly, individual models accounted for idiosyncrasies in behavior or inconsistencies in sensor placement for those sessions that group models could not generalize to.
